### 2024-08-17 paper.tex
why is irred
fix notation; move some stuff from section 7 to section 8

\[G_{wr} := \{P \in \GL_m : \forall b. \exists b'. (P^{-1}, I_n) A_{e_{wr}, b} (P, I_n) = A_{e_{wr}, b'}\}.\]
If you write out the condition \(A_{e_{wr}, b} (A, I_n) = (A, I_n) A_{X, e_{wr}, b'}\) as a matrix equation, it is plain to see that 

@@

\[U_{wr} = \{(U, e_{wr}, b) \in V_{wr}\}.\]

@@

    not sure why at the moment

@@

\par To do this, we will use a known result about the irreducible components of the usual Springer fiber at an element \(J(\mu) \in \gl_{m + n}\).
(I should define this somewhere else, but \(J(\mu)\) just has the blocks in order of nonincreasing size.)
\begin{theorem}
    (Needs citation!)
    The irreducible components of the Springer fiber at \(J(\mu)\) are in bijection with the standard Young tableaus of shape \(\mu\).
    Further, the irreducible components are equidimensional, of dimension \(\sum_{i \neq j} \min(\mu_i, \mu_j) = \sum_i (i - 1) \mu_i\).
\end{theorem}
Let \(W_\mu\) denote the Springer fiber at \(J(\mu)\), and let \((W_{\mu, d})_d\) be the irreducible components.
We remark that the Springer fiber at \(PJ(\mu)P^{-1}\) is \(PW_\mu\), and its irreducible components are \((PW_{\mu, d})_d\).
We will use this result; to find the regular Springer fiber at any \(X \in \gl_{m + n}\), we just need to find \(P\) such that \(P^{-1}XP\) is in Jordan normal form; equivalently, we just need to find a Jordan basis for \(X\).
So, our strategy will be to find a subset of \(U_{wr}\) such that \(A_{e_{wr},b}\) has some fixed Jordan form \(\mu\), and the map \(b \mapsto P\) is algebraic.
Then we can break this subset into irreducible components by putting the Springer fiber at \(b\) in correspondence with one of the \(W_{\mu,d}\).
I think this explanation of intuition is important, so I should try to make it better.
\par So, with this as our motivation, we find a Jordan basis for the matrices \(A\) with \((A, U) \in U_{wr}\).
Actually this will be unnecessarily difficult to think about; it is easiest in the case \(r = 0\).

@@

\section{Finding the irreducible components of \(U\)}
Let \(X\) be nilpotent of shape \(\lambda\), etc.
Start fresh finding irreducible components of \(U_{w0}\).

>>>>

@@

\[U_{wr} = \{(A_{e_{wr}, b}, U) \in V_{wr}\}.\]

@@

    It's just \(\mathbb{C}^{something}\), since its blocks are the lower-left-toeplitz matrices.

@@

\par Actually this will be unnecessarily difficult to think about; it is easiest in the case \(r = 0\).

@@

\section{Finding the irreducible components of \(U_0\)}
Let \(X\) be nilpotent of shape \(\lambda\).
Let 
\[U_0 = \{\]
Start fresh finding irreducible components of \(U_{w0}\).
\par To do this, we will use a known result about the irreducible components of the usual Springer fiber at an element \(J(\mu) \in \gl_{m + n}\).
(I should define this somewhere else, but \(J(\mu)\) just has the blocks in order of nonincreasing size.)
\begin{theorem}
    (Needs citation!)
    The irreducible components of the Springer fiber at \(J(\mu)\) are in bijection with the standard Young tableaus of shape \(\mu\).
    Further, the irreducible components are equidimensional, of dimension \(\sum_{i \neq j} \min(\mu_i, \mu_j) = \sum_i (i - 1) \mu_i\).
\end{theorem}
Let \(W_\mu\) denote the Springer fiber at \(J(\mu)\), and let \((W_{\mu, d})_d\) be the irreducible components.
We remark that the Springer fiber at \(PJ(\mu)P^{-1}\) is \(PW_\mu\), and its irreducible components are \((PW_{\mu, d})_d\).
We will use this result; to find the regular Springer fiber at any \(X \in \gl_{m + n}\), we just need to find \(P\) such that \(P^{-1}XP\) is in Jordan normal form; equivalently, we just need to find a Jordan basis for \(X\).
So, our strategy will be to find a subset of \(U_{wr}\) such that \(A_{e_{wr},b}\) has some fixed Jordan form \(\mu\), and the map \(b \mapsto P\) is algebraic.
Then we can break this subset into irreducible components by putting the Springer fiber at \(b\) in correspondence with one of the \(W_{\mu,d}\).
I think this explanation of intuition is important, so I should try to make it better.
\par So, with this as our motivation, we find a Jordan basis for the matrices \(A\) with \((A, U) \in U_{wr}\).
